Preprocess turk annotations

### 2020-01-11 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
preprocessing turk segmentations

---
title: "Preprocess turk annotations ="
output: html_notebook
---

@@

``
# Preprocessing

```{r}
f <- dir("turk_annotations_segmentation/")
jf <- paste("turk_annotations_segmentation/",f,sep="")
jd <- read_csv(jf)

d.raw <- data.frame()
trial_indexes = seq(1,200,1)
  for (trial_ind in trial_indexes){
    ## get annotation and see if empty
    this_annotation = jd$Answer.annotatedResult.boundingBoxes[trial_ind]
    cleaned_annotation = fromJSON(this_annotation)

@@

### Write out csv for use in analysis
```{r}
write_csv(d,'turk_segmentations_dec12.csv')
```

@@

  annotated_file = paste0(unique(a$short_image_path), 'turk-annotated.jpg')
  image_write(img, annotated_file)
  dev.off()
}

>>>>

---
title: "Preprocess turk annotations"
output: html_notebook
---

@@

# Preprocessing

```{r}
# f <- dir("turk_annotations_segmentation/")
# jf <- paste("turk_annotations_segmentation/",f,sep="")
# jd <- read_csv(jf)

f = "turk_segmentations_hands_only.csv"
jf <- paste("../../../data/",f,sep="")
jd <- read_csv(jf)

d.raw <- data.frame()
trial_indexes = seq(1,length(jd$Input.img_src1),1)
  for (trial_ind in trial_indexes){
    ## get annotation and see if empty
    this_annotation = jd$Answer.annotatedResult.boundingBoxes[trial_ind]
    cleaned_annotation = fromJSON(this_annotation)

@@

```{r}

d <- d.raw %>%
  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Adult Face")) %>%
  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  rowwise() %>%
  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1]) 
```

### How many frames/videos had children's faces?
```{r}
child_face_frames <- d %>%
  filter(label=="Child face")

# render out some of these...
# dir.create(paste0('child_face/'))
# for (i in seq(1,length(child_face_frames$full_image_path),1)){
#   image_read(as.character(child_face_frames$full_image_path[i])) %>%
#   image_append(stack = FALSE) %>%
#   image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
# }

# dir.create(paste0('annotated-images-child-face/'))
# unique_images = child_face_frames$full_image_path
# for (image in unique_images){
#   this_image_rgb <- image_read(image)
#   img <- image_draw(this_image_rgb)
#   a <- d %>%
#     filter(full_image_path %in% image) 
#   
### rect(xleft, ybottom, xright, ytop
#   rect(a$left, a$top+a$height, a$left+a$width, a$top)
#   text(a$left+10, a$top+10, a$label)
#   
#   annotated_file = paste0('annotated-images-child-face/',unique(a$short_image_path), 'turk-annotated.jpg')
#   image_write(img, annotated_file)
#   dev.off()
# }

### Write out csv for use in analysis
```{r}
write_csv(d,'turk_segmentations_hands_only_processed.csv')
```

@@

  annotated_file = paste0('annotated-images/',unique(a$short_image_path), 'turk-annotated.jpg')
  image_write(img, annotated_file)
  dev.off()
}
